---
title: "Flow state analysis 3-1-23"
author: "Julia Zielke"
date: "3/1/2023"
output: html_document
---

# Setup

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidyr)
library(dplyr)
library(readxl)
library(stats)
library(janitor)
library(qualtRics)
library(psych)
library(lm.beta)
```

# Data prep

Importing raw data:
```{r, echo=TRUE}
# Importing a Qualtrics-generated .csv file in a way that takes care of variable names/labels:
data_raw <- as_tibble(
  qualtRics::read_survey("flow-associations-analysis/data/Flow Data.csv"))
                        
    #25 participants, total, 20 have valid data

```

#Initial Processing of Qualtrics Data
Throwing out testing IDs and removing unnecessary variables, removing invalid or incomplete participant data.

```{r, echo=TRUE}
data_processed <- data_raw |>
 #removing unnecessary variables
   select(-StartDate, -EndDate, -Progress, -`Duration (in seconds)`, -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -ExternalReference) 
#throw out testing ids; testing id = 1
data_processed <- data_processed %>%
  filter(Status != 1) %>%
  #throw out incomplete or invalid responses (participants who did not submit a score or did not experience flow)
  filter(data_valid != 0)
#removes 5 participants

data_processed <- data_processed |>
 #removing unnecessary variables for analysis 
  #consent - Q15 & Q13
  #Distractor task responses - Q1, Q2, Q3)
  #testing ids - Status
   select(-Status, -Q15, -Q13, -Q1, -Q2, -Q3) 
  
```

#Demographics
Age
```{r}
mean_age <- mean(data_processed$Age)
print(mean_age)

sd_age <- sd(data_processed$Age)
print(sd_age)
```

How long participants have been playing their instrument
```{r}
mean_played <- mean(data_processed$YearsPlayed)
print(mean_played)

sd_played <- sd(data_processed$YearsPlayed)
print(sd_played)
```

#Scoring Flow Scale (FSS)

```{r}
data_processed <- data_processed %>%
  rename(Flow_1 = `Flow Short Scale_1`,
         Flow_2 = `Flow Short Scale_2`,
         Flow_3 = `Flow Short Scale_3`,
         Flow_4 = `Flow Short Scale_4`,
         Flow_5 = `Flow Short Scale_5`,
         Flow_6 = `Flow Short Scale_6`,
         Flow_7 = `Flow Short Scale_7`,
         Flow_8 = `Flow Short Scale_8`,
         Flow_9 = `Flow Short Scale_9`,
         Flow_10 = `Flow Short Scale_10`) %>%
  #taking mean of FSS items for each participant (row)
   mutate(flow = rowMeans(
             subset(., select = c(Flow_1:Flow_10))))
```

#Calculating the Difference between Time estimate and Actual time (time distortion)
```{r}
data_processed <- data_processed %>%
  #coercing variables to numeric for calculation
  mutate(actual_time = as.numeric(actual_time)) %>%
  mutate(time_estimate_sec = as.numeric(time_estimate_sec)) %>%
  mutate(time_flow = as.numeric(time_flow)) %>%
  #time distortion operationalized as the difference between time estimate and actual time
  mutate(time_diff = as.numeric(time_estimate_sec) - as.numeric(actual_time))
```

#Summary of Variables Data Table
```{r}
#selecting variables to summarize
data_table_1 <- data_processed[, c(31:33, 35:36)]

#putting flow first for cosmetics
data_table_1 <- data_table_1 %>%
  relocate(flow, .before = time_estimate_sec)

summary(data_table_1)

#A proportion of the total performance time will be used to look at flow duration instead of a flat value since the reported flow time durations varied greatly (range: 5 seconds to 175 seconds, mean: 46.9 seconds).

```

#Proportion of time in flow
```{r}
data_processed <- data_processed %>%
   mutate(time_flow_proportion = time_flow/actual_time)
```

Creating an easier to read table that summarizes variables
```{r}
library(table1)

#adding proportion of time in flow to table dataframe
data_table_1 <- data_table_1 %>%
   mutate(time_flow_proportion = time_flow/actual_time)

table1::label(data_table_1$flow) <- "FSS"
table1::label(data_table_1$time_estimate_sec) <- "Time estimate (sec)"
table1::label(data_table_1$actual_time) <- "Actual time (sec)"
table1::label(data_table_1$time_diff) <- "Time difference (sec)"
table1::label(data_table_1$time_flow) <- "Duration of time in flow (sec)"
table1::label(data_table_1$time_flow_proportion) <- "Proportion of time in flow"
table1::table1(~flow + time_estimate_sec + actual_time + time_diff + time_flow + time_flow_proportion, data = data_table_1)
```

#Analyses:

Time distortion
```{r}
lm_1 = lm(time_diff~flow, data = data_processed) 
summary(lm_1)

#Result: no significant association between FSS score and time distortion, p = 0.6743

cor.test(data_processed$time_diff, data_processed$flow)
#correlation = -0.100

ggplot(data_processed, aes(x = flow, y = time_diff)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Time distortion and state flow") +
  ylab("Time distortion") +
  xlab("State flow (FSS)") +
  theme_light()
```
proportion of time in flow (flow duration)
```{r}
lm_2 = lm(time_flow_proportion~flow, data = data_processed) 
summary(lm_2)

# Result: significant positive association between FSS score and flow duration, p = 0.009864

cor.test(data_processed$time_flow_proportion, data_processed$flow)
#correlation = 0.56

ggplot(data_processed, aes(x = flow, y = time_flow_proportion)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Flow duration and state flow") +
  ylab("Flow duration") +
  xlab("State flow (FSS)") +
  theme_light()

```

#Calculating Cronbach's Alpha for FSS
```{r}
data_alpha <- data_processed[,c(1:10)]

alpha(data_alpha)
#cronbach's alpha = 0.87
```

Summary stats of FSS score
```{r}
#mean
mean(data_processed$flow)

#sd
sd(data_processed$flow)

# mean 4.74 (SD =  0.99)
```



#Flow subscales: Absorption 
```{r}
#selecting only the variables for the absorption subscale along with the dependent variables
data_absorption <- data_processed[,c(1, 3, 6, 10, 34, 35, 36, 37)]

#calculating absorption subscore
data_absorption <- data_absorption %>%
   mutate(flow = rowMeans(
             subset(., select = c(Flow_1:Flow_10)))) 

#Cronbach's alpha
data_alpha_absorption <- data_absorption[,c(1:4)]

alpha(data_alpha_absorption)

# α = 0.56

#mean
mean(data_absorption$flow)

#sd
sd(data_absorption$flow)

#subscore mean 4.3 (SD = 0.99) 
```

#Absorption analyses:

Time distortion
```{r}
lm_3 = lm(time_diff~flow, data = data_absorption) 
summary(lm_3)

#Result: no significant association between absorption and time distortion, p = 0.8305

cor.test(data_absorption$time_diff, data_absorption$flow)
#correlation = 0.051

ggplot(data_absorption, aes(x = flow, y = time_diff)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Time distortion and absorption") +
  ylab("Time distortion") +
  xlab("Absorption (FSS)") +
  theme_light()
```

Flow duration
```{r}
lm_4 = lm(time_flow_proportion~flow, data = data_absorption) 
summary(lm_4)

#Result: no significant association between absorption and flow duration, p = 0.1102

cor.test(data_absorption$time_flow_proportion, data_absorption$flow)
#correlation = 0.368

ggplot(data_absorption, aes(x = flow, y = time_flow_proportion)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Flow duration and absorption") +
  ylab("Flow duration") +
  xlab("Absorption (FSS)") +
  theme_light()
```

#Flow subscales: Fluency
```{r}
#selecting only the variables for the fluency subscale along with the dependent variables
data_fluency <- data_processed[,c(2, 4, 5, 7, 8, 9, 34, 35, 36, 37)]

#calculating fluency subscore
data_fluency <- data_fluency %>%
   mutate(flow = rowMeans(
             subset(., select = c(Flow_2:Flow_9)))) 

#Cronbach's alpha
data_alpha_fluency <- data_fluency[,c(1:6)]

alpha(data_alpha_fluency)

# α = 0.91

#mean
mean(data_fluency$flow)

#sd
sd(data_fluency$flow)

#subscore mean 5.03 (SD = 1.20)
```

#Fluency analyses:
```{r}
lm_5 = lm(time_diff~flow, data = data_fluency) 
summary(lm_5)

#Result: no significant association between fluency and time distortion, p = 0.4857

cor.test(data_fluency$time_diff, data_fluency$flow)
#correlation = -0.165

ggplot(data_fluency, aes(x = flow, y = time_diff)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Time distortion and Fluency") +
  ylab("Time distortion") +
  xlab("Fluency (FSS)") +
  theme_light()
```

Flow duration
```{r}
lm_6 = lm(time_flow_proportion ~ flow, data = data_fluency) 
summary(lm_6)

#Result: significant positive association between fluency and flow duration, p = 0.008775

cor.test(data_fluency$time_flow_proportion, data_fluency$flow)
#correlation = 0.569

ggplot(data_fluency, aes(x = flow, y = time_flow_proportion)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se=FALSE) +
  ggtitle("Flow duration and fluency") +
  xlab("Fluency (FSS)") +
  ylab("Flow duration")

```