---
title: "flow analysis midi"
author: "Julia Zielke"
date: "2/14/2023"
output: html_document
---

#Setup
```{r packages}
knitr::opts_chunk$set(echo = TRUE)

if(!suppressWarnings(require(pacman))){install.packages("pacman");library("pacman")}
p_load(tidyverse,
       tidyr,
       dplyr,
       stats,
       janitor,
       qualtRics,
       psych,
       stringr)

```
#Before Flow

##Transforming Data to a format ready to combine together for all the flow instances

##Participant 1
```{r}
# Importing .csv file:
p01_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p01_f01_b.csv", row.names=NULL))

#renaming the columns given by midi to .csv conversion
p01_f01_b <- p01_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

#removing unnecessary rows
p01_f01_b <- p01_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

#Removing control events
p01_f01_b <- p01_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

#removing unnecessary columns, must be done after control events are removed
p01_f01_b <- p01_f01_b[, -c(3, 4, 7)]

#removing note stops
p01_f01_b <- p01_f01_b %>%
  filter(note_velocity != 0)

#creating a melody degree variable, also sorts melody_degree to the front of the dataframe
p01_f01_b <- p01_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

#this will change the melody id for every participant and flow instance after this. This is the first one, so the ID remains 1.
p01_f01_b <- p01_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  1, melody_id)))

#creating participant id variable to nest the melodies within
p01_f01_b <- p01_f01_b %>%
  mutate(participant_id = 1)

#adding bar numbers of the flow instance from Qualtrics data
p01_f01_b <- p01_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file
p01_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p01_f02_b.csv", row.names=NULL))

p01_f02_b <- p01_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p01_f02_b <- p01_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p01_f02_b <- p01_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p01_f02_b <- p01_f02_b[, -c(3, 4, 7)]

p01_f02_b <- p01_f02_b %>%
  filter(note_velocity != 0)

p01_f02_b <- p01_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p01_f02_b <- p01_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  2, melody_id)))

p01_f02_b <- p01_f02_b %>%
  mutate(participant_id = 1)

p01_f02_b <- p01_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 2
```{r}
# Importing .csv file:
p02_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p02_f01_b.csv", row.names=NULL))

p02_f01_b <- p02_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p02_f01_b <- p02_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p02_f01_b <- p02_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p02_f01_b <- p02_f01_b[, -c(3, 4, 7)]

p02_f01_b <- p02_f01_b %>%
  filter(note_velocity != 0)

p02_f01_b <- p02_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p02_f01_b <- p02_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  3, melody_id)))

p02_f01_b <- p02_f01_b %>%
  mutate(participant_id = 2)

p02_f01_b <- p02_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file
p02_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p02_f02_b.csv", row.names=NULL))

p02_f02_b <- p02_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p02_f02_b <- p02_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p02_f02_b <- p02_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p02_f02_b <- p02_f02_b[, -c(3, 4, 7)]

p02_f02_b <- p02_f02_b %>%
  filter(note_velocity != 0)

p02_f02_b <- p02_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p02_f02_b <- p02_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  4, melody_id)))

p02_f02_b <- p02_f02_b %>%
  mutate(participant_id = 2)

p02_f02_b <- p02_f02_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file
p02_f03_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p02_f03_b.csv", row.names=NULL))

p02_f03_b <- p02_f03_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p02_f03_b <- p02_f03_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p02_f03_b <- p02_f03_b %>%
  filter(!str_detect(X0.1, "Control"))

p02_f03_b <- p02_f03_b[, -c(3, 4, 7)]

p02_f03_b <- p02_f03_b %>%
  filter(note_velocity != 0)

p02_f03_b <- p02_f03_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p02_f03_b <- p02_f03_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  5, melody_id)))

p02_f03_b <- p02_f03_b %>%
  mutate(participant_id = 2)

p02_f03_b <- p02_f03_b %>%
  mutate(bar_number = 4)
```


###Participant 3
```{r}
# Importing .csv file:
p03_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p03_f01_b.csv", row.names=NULL))

p03_f01_b <- p03_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p03_f01_b <- p03_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p03_f01_b <- p03_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p03_f01_b <- p03_f01_b[, -c(3, 4, 7)]

p03_f01_b <- p03_f01_b %>%
  filter(note_velocity != 0)

p03_f01_b <- p03_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p03_f01_b <- p03_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  6, melody_id)))

p03_f01_b <- p03_f01_b %>%
  mutate(participant_id = 3)

p03_f01_b <- p03_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file
p03_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p03_f02_b.csv", row.names=NULL))

p03_f02_b <- p03_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p03_f02_b <- p03_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p03_f02_b <- p03_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p03_f02_b <- p03_f02_b[, -c(3, 4, 7)]

p03_f02_b <- p03_f02_b %>%
  filter(note_velocity != 0)

p03_f02_b <- p03_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p03_f02_b <- p03_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  7, melody_id)))

p03_f02_b <- p03_f02_b %>%
  mutate(participant_id = 3)

p03_f02_b <- p03_f02_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file
p03_f03_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p03_f03_b.csv", row.names=NULL))

p03_f03_b <- p03_f03_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p03_f03_b <- p03_f03_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p03_f03_b <- p03_f03_b %>%
  filter(!str_detect(X0.1, "Control"))

p03_f03_b <- p03_f03_b[, -c(3, 4, 7)]

p03_f03_b <- p03_f03_b %>%
  filter(note_velocity != 0)

p03_f03_b <- p03_f03_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p03_f03_b <- p03_f03_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  8, melody_id)))

p03_f03_b <- p03_f03_b %>%
  mutate(participant_id = 3)

p03_f03_b <- p03_f03_b %>%
  mutate(bar_number = 4)
```

##Participant 4
```{r}
# Importing .csv file:
p04_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p04_f01_b.csv", row.names=NULL))

p04_f01_b <- p04_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p04_f01_b <- p04_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p04_f01_b <- p04_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p04_f01_b <- p04_f01_b[, -c(3, 4, 7)]

p04_f01_b <- p04_f01_b %>%
  filter(note_velocity != 0)

p04_f01_b <- p04_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p04_f01_b <- p04_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  9, melody_id)))

p04_f01_b <- p04_f01_b %>%
  mutate(participant_id = 4)

p04_f01_b <- p04_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 5
```{r}
# Importing .csv file:
p05_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p05_f01_b.csv", row.names=NULL))

p05_f01_b <- p05_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p05_f01_b <- p05_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p05_f01_b <- p05_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p05_f01_b <- p05_f01_b[, -c(3, 4, 7)]

p05_f01_b <- p05_f01_b %>%
  filter(note_velocity != 0)

p05_f01_b <- p05_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p05_f01_b <- p05_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  10, melody_id)))

p05_f01_b <- p05_f01_b %>%
  mutate(participant_id = 5)

p05_f01_b <- p05_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 6
```{r}
# Importing .csv file:
p06_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p06_f01_b.csv", row.names=NULL))

p06_f01_b <- p06_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p06_f01_b <- p06_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p06_f01_b <- p06_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p06_f01_b <- p06_f01_b[, -c(3, 4, 7)]

p06_f01_b <- p06_f01_b %>%
  filter(note_velocity != 0)

p06_f01_b <- p06_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p06_f01_b <- p06_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  11, melody_id)))

p06_f01_b <- p06_f01_b %>%
  mutate(participant_id = 6)

p06_f01_b <- p06_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p06_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p06_f02_b.csv", row.names=NULL))

p06_f02_b <- p06_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p06_f02_b <- p06_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p06_f02_b <- p06_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p06_f02_b <- p06_f02_b[, -c(3, 4, 7)]

p06_f02_b <- p06_f02_b %>%
  filter(note_velocity != 0)

p06_f02_b <- p06_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p06_f02_b <- p06_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  12, melody_id)))

p06_f02_b <- p06_f02_b %>%
  mutate(participant_id = 6)

p06_f02_b <- p06_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 7
```{r}
# Importing .csv file:
p07_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p07_f01_b.csv", row.names=NULL))

p07_f01_b <- p07_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p07_f01_b <- p07_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p07_f01_b <- p07_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p07_f01_b <- p07_f01_b[, -c(3, 4, 7)]

p07_f01_b <- p07_f01_b %>%
  filter(note_velocity != 0)

p07_f01_b <- p07_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p07_f01_b <- p07_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  13, melody_id)))

p07_f01_b <- p07_f01_b %>%
  mutate(participant_id = 7)

p07_f01_b <- p07_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p07_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p07_f02_b.csv", row.names=NULL))

p07_f02_b <- p07_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p07_f02_b <- p07_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p07_f02_b <- p07_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p07_f02_b <- p07_f02_b[, -c(3, 4, 7)]

p07_f02_b <- p07_f02_b %>%
  filter(note_velocity != 0)

p07_f02_b <- p07_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p07_f02_b <- p07_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  14, melody_id)))

p07_f02_b <- p07_f02_b %>%
  mutate(participant_id = 7)

p07_f02_b <- p07_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 8
```{r}
# Importing .csv file:
p08_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p08_f01_b.csv", row.names=NULL))

p08_f01_b <- p08_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p08_f01_b <- p08_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p08_f01_b <- p08_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p08_f01_b <- p08_f01_b[, -c(3, 4, 7)]

p08_f01_b <- p08_f01_b %>%
  filter(note_velocity != 0)

p08_f01_b <- p08_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p08_f01_b <- p08_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  15, melody_id)))

p08_f01_b <- p08_f01_b %>%
  mutate(participant_id = 8)

p08_f01_b <- p08_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 9
```{r}
# Importing .csv file:
p09_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p09_f01_b.csv", row.names=NULL))

p09_f01_b <- p09_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p09_f01_b <- p09_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p09_f01_b <- p09_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p09_f01_b <- p09_f01_b[, -c(3, 4, 7)]

p09_f01_b <- p09_f01_b %>%
  filter(note_velocity != 0)

p09_f01_b <- p09_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p09_f01_b <- p09_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  16, melody_id)))

p09_f01_b <- p09_f01_b %>%
  mutate(participant_id = 9)

p09_f01_b <- p09_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p09_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p09_f02_b.csv", row.names=NULL))

p09_f02_b <- p09_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p09_f02_b <- p09_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p09_f02_b <- p09_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p09_f02_b <- p09_f02_b[, -c(3, 4, 7)]

p09_f02_b <- p09_f02_b %>%
  filter(note_velocity != 0)

p09_f02_b <- p09_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p09_f02_b <- p09_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  17, melody_id)))

p09_f02_b <- p09_f02_b %>%
  mutate(participant_id = 9)

p09_f02_b <- p09_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 10
```{r}
# Importing .csv file:
p10_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p10_f01_b.csv", row.names=NULL))

p10_f01_b <- p10_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p10_f01_b <- p10_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p10_f01_b <- p10_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p10_f01_b <- p10_f01_b[, -c(3, 4, 7)]

p10_f01_b <- p10_f01_b %>%
  filter(note_velocity != 0)

p10_f01_b <- p10_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p10_f01_b <- p10_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  18, melody_id)))

p10_f01_b <- p10_f01_b %>%
  mutate(participant_id = 10)

p10_f01_b <- p10_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p10_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p10_f02_b.csv", row.names=NULL))

p10_f02_b <- p10_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p10_f02_b <- p10_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p10_f02_b <- p10_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p10_f02_b <- p10_f02_b[, -c(3, 4, 7)]

p10_f02_b <- p10_f02_b %>%
  filter(note_velocity != 0)

p10_f02_b <- p10_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p10_f02_b <- p10_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  19, melody_id)))

p10_f02_b <- p10_f02_b %>%
  mutate(participant_id = 10)

p10_f02_b <- p10_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 11
```{r}
# Importing .csv file:
p11_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p11_f01_b.csv", row.names=NULL))

p11_f01_b <- p11_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p11_f01_b <- p11_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p11_f01_b <- p11_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p11_f01_b <- p11_f01_b[, -c(3, 4, 7)]

p11_f01_b <- p11_f01_b %>%
  filter(note_velocity != 0)

p11_f01_b <- p11_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p11_f01_b <- p11_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  20, melody_id)))

p11_f01_b <- p11_f01_b %>%
  mutate(participant_id = 11)

p11_f01_b <- p11_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 12
```{r}
# Importing .csv file:
p12_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p12_f01_b.csv", row.names=NULL))

p12_f01_b <- p12_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p12_f01_b <- p12_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p12_f01_b <- p12_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p12_f01_b <- p12_f01_b[, -c(3, 4, 7)]

p12_f01_b <- p12_f01_b %>%
  filter(note_velocity != 0)

p12_f01_b <- p12_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p12_f01_b <- p12_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  21, melody_id)))

p12_f01_b <- p12_f01_b %>%
  mutate(participant_id = 12)

p12_f01_b <- p12_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p12_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p12_f02_b.csv", row.names=NULL))

p12_f02_b <- p12_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p12_f02_b <- p12_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p12_f02_b <- p12_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p12_f02_b <- p12_f02_b[, -c(3, 4, 7)]

p12_f02_b <- p12_f02_b %>%
  filter(note_velocity != 0)

p12_f02_b <- p12_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p12_f02_b <- p12_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  22, melody_id)))

p12_f02_b <- p12_f02_b %>%
  mutate(participant_id = 12)

p12_f02_b <- p12_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 13
```{r}
# Importing .csv file:
p13_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p13_f01_b.csv", row.names=NULL))

p13_f01_b <- p13_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p13_f01_b <- p13_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p13_f01_b <- p13_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p13_f01_b <- p13_f01_b[, -c(3, 4, 7)]

p13_f01_b <- p13_f01_b %>%
  filter(note_velocity != 0)

p13_f01_b <- p13_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p13_f01_b <- p13_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  23, melody_id)))

p13_f01_b <- p13_f01_b %>%
  mutate(participant_id = 13)

p13_f01_b <- p13_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p13_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p13_f02_b.csv", row.names=NULL))

p13_f02_b <- p13_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p13_f02_b <- p13_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p13_f02_b <- p13_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p13_f02_b <- p13_f02_b[, -c(3, 4, 7)]

p13_f02_b <- p13_f02_b %>%
  filter(note_velocity != 0)

p13_f02_b <- p13_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p13_f02_b <- p13_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  24, melody_id)))

p13_f02_b <- p13_f02_b %>%
  mutate(participant_id = 13)

p13_f02_b <- p13_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 14
```{r}
# Importing .csv file:
p14_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p14_f01_b.csv", row.names=NULL))

p14_f01_b <- p14_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p14_f01_b <- p14_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p14_f01_b <- p14_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p14_f01_b <- p14_f01_b[, -c(3, 4, 7)]

p14_f01_b <- p14_f01_b %>%
  filter(note_velocity != 0)

p14_f01_b <- p14_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p14_f01_b <- p14_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  25, melody_id)))

p14_f01_b <- p14_f01_b %>%
  mutate(participant_id = 14)

p14_f01_b <- p14_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p14_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p14_f02_b.csv", row.names=NULL))

p14_f02_b <- p14_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p14_f02_b <- p14_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p14_f02_b <- p14_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p14_f02_b <- p14_f02_b[, -c(3, 4, 7)]

p14_f02_b <- p14_f02_b %>%
  filter(note_velocity != 0)

p14_f02_b <- p14_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p14_f02_b <- p14_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  26, melody_id)))

p14_f02_b <- p14_f02_b %>%
  mutate(participant_id = 14)

p14_f02_b <- p14_f02_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p14_f03_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p14_f03_b.csv", row.names=NULL))

p14_f03_b <- p14_f03_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p14_f03_b <- p14_f03_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p14_f03_b <- p14_f03_b %>%
  filter(!str_detect(X0.1, "Control"))

p14_f03_b <- p14_f03_b[, -c(3, 4, 7)]

p14_f03_b <- p14_f03_b %>%
  filter(note_velocity != 0)

p14_f03_b <- p14_f03_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p14_f03_b <- p14_f03_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  27, melody_id)))

p14_f03_b <- p14_f03_b %>%
  mutate(participant_id = 14)

p14_f03_b <- p14_f03_b %>%
  mutate(bar_number = 4)
```

##Participant 15
```{r}
# Importing .csv file:
p15_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p15_f01_b.csv", row.names=NULL))

p15_f01_b <- p15_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p15_f01_b <- p15_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p15_f01_b <- p15_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p15_f01_b <- p15_f01_b[, -c(3, 4, 7)]

p15_f01_b <- p15_f01_b %>%
  filter(note_velocity != 0)

p15_f01_b <- p15_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p15_f01_b <- p15_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  28, melody_id)))

p15_f01_b <- p15_f01_b %>%
  mutate(participant_id = 15)

p15_f01_b <- p15_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 16
```{r}
# Importing .csv file:
p16_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p16_f01_b.csv", row.names=NULL))

p16_f01_b <- p16_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p16_f01_b <- p16_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p16_f01_b <- p16_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p16_f01_b <- p16_f01_b[, -c(3, 4, 7)]

p16_f01_b <- p16_f01_b %>%
  filter(note_velocity != 0)

p16_f01_b <- p16_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p16_f01_b <- p16_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  29, melody_id)))

p16_f01_b <- p16_f01_b %>%
  mutate(participant_id = 16)

p16_f01_b <- p16_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 17
```{r}
# Importing .csv file:
p17_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p17_f01_b.csv", row.names=NULL))

p17_f01_b <- p17_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p17_f01_b <- p17_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p17_f01_b <- p17_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p17_f01_b <- p17_f01_b[, -c(3, 4, 7)]

p17_f01_b <- p17_f01_b %>%
  filter(note_velocity != 0)

p17_f01_b <- p17_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p17_f01_b <- p17_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  30, melody_id)))

p17_f01_b <- p17_f01_b %>%
  mutate(participant_id = 17)

p17_f01_b <- p17_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 18
```{r}
# Importing .csv file:
p18_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p18_f01_b.csv", row.names=NULL))

p18_f01_b <- p18_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p18_f01_b <- p18_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p18_f01_b <- p18_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p18_f01_b <- p18_f01_b[, -c(3, 4, 7)]

p18_f01_b <- p18_f01_b %>%
  filter(note_velocity != 0)

p18_f01_b <- p18_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p18_f01_b <- p18_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  31, melody_id)))

p18_f01_b <- p18_f01_b %>%
  mutate(participant_id = 18)

p18_f01_b <- p18_f01_b %>%
  mutate(bar_number = 4)
```

##Participant 19
```{r}
# Importing .csv file:
p19_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p19_f01_b.csv", row.names=NULL))

p19_f01_b <- p19_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p19_f01_b <- p19_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p19_f01_b <- p19_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p19_f01_b <- p19_f01_b[, -c(3, 4, 7)]

p19_f01_b <- p19_f01_b %>%
  filter(note_velocity != 0)

p19_f01_b <- p19_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p19_f01_b <- p19_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  32, melody_id)))

p19_f01_b <- p19_f01_b %>%
  mutate(participant_id = 19)

p19_f01_b <- p19_f01_b %>%
  mutate(bar_number = 4)
```

```{r}
# Importing .csv file:
p19_f02_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p19_f02_b.csv", row.names=NULL))

p19_f02_b <- p19_f02_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p19_f02_b <- p19_f02_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p19_f02_b <- p19_f02_b %>%
  filter(!str_detect(X0.1, "Control"))

p19_f02_b <- p19_f02_b[, -c(3, 4, 7)]

p19_f02_b <- p19_f02_b %>%
  filter(note_velocity != 0)

p19_f02_b <- p19_f02_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p19_f02_b <- p19_f02_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  33, melody_id)))

p19_f02_b <- p19_f02_b %>%
  mutate(participant_id = 19)

p19_f02_b <- p19_f02_b %>%
  mutate(bar_number = 4)
```

##Participant 20
```{r}
# Importing .csv file:
p20_f01_b <- as.tibble(
  read.csv(
    "Excerpts/Midi/p20_f01_b.csv", row.names=NULL))

p20_f01_b <- p20_f01_b %>%
  rename(melody_id = row.names, 
         note_onset = X0,
         note_midi_value = X1,
         note_velocity = X1.1
           ) 

p20_f01_b <- p20_f01_b[-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),]

p20_f01_b <- p20_f01_b %>%
  filter(!str_detect(X0.1, "Control"))

p20_f01_b <- p20_f01_b[, -c(3, 4, 7)]

p20_f01_b <- p20_f01_b %>%
  filter(note_velocity != 0)

p20_f01_b <- p20_f01_b %>%
  mutate(melody_degree
= row_number()) %>%
  relocate(melody_degree, .after = melody_id)

p20_f01_b <- p20_f01_b %>% 
  mutate_at(.vars = vars(melody_id),
             .funs = list(~ifelse((melody_id
  == 1),
  34, melody_id)))

p20_f01_b <- p20_f01_b %>%
  mutate(participant_id = 20)

p20_f01_b <- p20_f01_b %>%
  mutate(bar_number = 4)
```

#Combining all events together
```{r}
all_df <- rbind(p01_f01_b, 
                p01_f02_b, 
                p02_f01_b, 
                p02_f02_b, 
                p02_f03_b,
                p03_f01_b, 
                p03_f02_b, 
                p03_f03_b,
                p04_f01_b,
                p05_f01_b,
                p06_f01_b,
                p06_f02_b,
                p07_f01_b,
                p07_f02_b,
                p08_f01_b,
                p09_f01_b,
                p09_f02_b,
                p10_f01_b,
                p10_f02_b,
                p11_f01_b,
                p12_f01_b,
                p12_f02_b,
                p13_f01_b,
                p13_f02_b,
                p14_f01_b,
                p14_f02_b,
                p14_f03_b,
                p15_f01_b,
                p16_f01_b,
                p17_f01_b,
                p18_f01_b,
                p19_f01_b,
                p19_f02_b,
                p20_f01_b
                )
```

#Write .csv
```{r exporting recoded data as a .csv file, echo=TRUE}
write_csv(all_df, "features-analysis/data/midi_flow_before.csv")
```


